### 2019-03-31 Thesis/games.tex
Daily commit.

@@

This time, instead of defining a relation $\Gamma,s\ts M\converges c,s'$, we define a relation $\Gamma,s\ts M\opto \Gamma',s'\ts M'$, where
\begin{itemize}
  \item $\Gamma,\Gamma'$ are $\Var$-contexts; 
  \item $s$ is a $\Gamma$-store and $s'$ a $\Gamma'$-store;  and
  \item $\Gamma\ts M$, $\Gamma'\ts M'$ are Idealized Algol terms-in-context.
\end{itemize}

@@

Next, we define a relation $\Gamma,s,M\oopto\Gamma',s',M'$ as in Figure \ref{FigIaSsOpSem}.

We then define the relation $\opto$ as
\[
  \inferrule*{ \Gamma,s\ts M\oopto \Gamma',s'\ts M'}{\Gamma,s\ts \EE[M] \opto \EE[M']}
  \]
for each evaluation context $\EE$.

\begin{figure}
  \begin{mathpar}
    \Gamma,s\ts (\lambda x.M)N \oopto \Gamma,s\ts M[N/x]
    \and
    \Gamma,s\ts \Y M \oopto \Gamma,s\ts M(\Y M)
    \and
    \Gamma,s\ts \suc n \oopto \Gamma,s\ts n+1
    \\
    \Gamma,s \ts \pred n+1 \oopto \Gamma,s\ts n
    \and
    \Gamma,s\ts \pred 0 \oopto \Gamma,s\ts 0
    \\
    \Gamma,s\ts \skipp;M \oopto \Gamma,s\ts M
    \\
    \Gamma,s\ts \If \true \Then N \Else P \oopto \Gamma,s\ts N
    \and
    \Gamma,s\ts \If \false \Then N \Else P \oopto \Gamma,s\ts P
    \and
    \Gamma,s\ts \IfO 0 \Then N \Else P \oopto \Gamma,s\ts N
    \and
    \Gamma,s\ts \IfO n+1 \Then N \Else P \oopto \Gamma,s\ts P
    \and
    \Gamma,s\ts x \gets n \oopto \Gamma,(s\vert x\mapsto n)\ts \skipp
    \and
    \Gamma,s\ts \oc x \oopto \Gamma,s\ts s(x)
    \\
    \Gamma,s\ts \neww \lambda x.M \oopto \Gamma,x,(s\vert x\mapsto 0)\ts M
    \\
    \Gamma,s \ts (\mkvar W\,R) \gets n \oopto \Gamma,s\ts Wn
    \and
    \Gamma,s \ts \oc(\mkvar W\,R) \oopto \Gamma,s\ts R
  \end{mathpar}
  \caption{Felleisen-style small-step operational semantics for Idealized Algol.}
  \label{FigIaSsOpSem}
\end{figure}

We need to prove that this is equivalent to our original semantics.
Given a $\Gamma'$-store $s$, and a sub-context $\Gamma$ of $\Gamma'$, write $s\vert_{\Gamma}$ for the restriction of $s$ to $\Gamma$.

\begin{lemma}
  Suppose that $\Gamma,s\ts M \oopto \Gamma',s'\ts M'$ and that $\Gamma',s'\ts \EE[M'] \converges c,s''$.  
  Then $\Gamma,s\ts \EE[M]\converges c,s''\vert_\Gamma$.
  \label{LemSmallToBig}
\end{lemma}
\begin{proof}
  Structural induction on $\EE$.
  The base case, when $\EE$ is a hole, covers the interesting cases, so we shall leave it to last.
  The remaining cases are quite similar, so we will show the proof for one of them for illustration.

  If $\EE=\EE'\,N$, for some term $N$, then we have $\Gamma',s'\ts \EE'[M']\,N\converges c,s''$.  
  By inspection of the rules in Figure \ref{FigIaOpSem}, the derivation of this must end with a rule of the form
  \[
    \inferrule*{\Gamma',s'\ts \EE'[M'] \converges \lambda x.M'',t \\ \Gamma',t \ts M''[N/x] \converges c,s''}
    {\Gamma',s'\ts \EE'[M']\,N \converges c,s''}\,.
    \]
  Thus, $\Gamma',s'\ts \EE'[M']\converges \lambda x.M'',t$ must be provable for some $M'',t$.
  By the induction hypothesis, this means that $\Gamma,s\ts \EE'[M]\converges \lambda x.M'',t$ is provable.
  Then we have a derivation
  \[
    \inferrule*{\Gamma',s\ts \EE'[M] \converges \lambda x.M'',t \\ \Gamma',t \ts M''[N/x] \converges c,s''}
    {\Gamma',s\ts \EE'[M]\,N\converges c,s''\vert_{\Gamma'}}\,.
    \]
  Then, because any extra variables in $\Gamma'$ are not mentioned in $\EE'[M]\,N$ or in $c$, we have
  \[
    \Gamma,s\ts \EE'[M]\,N\converges c,s''\vert_\Gamma\,.
    \]
  Now, let us suppose that $\EE$ is a hole, so that $\EE[M']=M'$.

@@

  \begin{itemize}
    \item Suppose that the last step in the derivation is
      \[
        \inferrule*{ }
        {\Gamma,s\ts c\converges c,s}\,.
        \]
      Then we have the one-element sequence $\Gamma,s\ts c$.  
    \item Suppose that the last step in the derivation is
      \[
        \inferrule*
        {
          \Gamma,s\ts M\converges \lambda x.M',s' \\ \Gamma,s' \ts M'[N/x]\converges c,s''
        }
        {
          \Gamma,s \ts MN\converges c,s''
        }\,.
        \]
      Then, by the inductive hypothesis, we have small-step derivations
      \begin{mathpar}
        \Gamma,s \ts M \opto \cdots \opto \Gamma',t',\lambda x.M'
        \and
        \Gamma,s' \ts M'[N/x]\opto \cdots \opto \Gamma'',t'',c\,,
      \end{mathpar}
      where $t'\vert_\Gamma=s'$ and $t''\vert_\Gamma=s''$.

      If we apply the evaluation context $-N$ pointwise to the first small-step derivation, then we have another valid small-step derivation.  
      Then we can join the two together to get the derivation
      \begin{center}
        \parbox{0.8\textwidth}{
        \begin{mathpar}
          \Gamma,s \ts MN \opto \cdots \opto \Gamma',t',(\lambda x.M')N \opto \Gamma',t',M'[N/x] \opto \cdots \opto \Gamma'\cup\Gamma'',t''\setminus t',c\,,
        \end{mathpar}}
      \end{center}
      where $t''\setminus t'$ is the $\Gamma'\cup\Gamma''$-store that agrees with $t''$ on $\Gamma''$ and with $t'$ on $\Gamma'\setminus\Gamma''$.
      Then $(t''\setminus t')\vert_{\Gamma}=s''$.
    \item Suppose that the last step in the derivation is
      \[
        \inferrule*
        {
          \Gamma,s\ts E\converges n,s' \\ \Gamma,s'\ts V\converges x,s''
        }
        {
          \Gamma,s \ts V \gets E \converges\skipp,(s''\vert x\mapsto n)
        }\,.
        \]
      By the inductive hypothesis, we have small-step derivations
      \begin{mathpar}
        \Gamma,s\ts E \opto \cdots \opto \Gamma',t',n
        \and
        \Gamma,s'\ts V \opto \cdots \opto \Gamma'',t'',x\,,
      \end{mathpar}
      where $t'\vert_{\Gamma}=s'$ and $t''\vert_{\Gamma}=s''$.

      We may apply the evaluation context $V\gets-$ pointwise to the first derivation and the evaluation context $-\gets n$ pointwise to the second, and then string the two together to get
      \begin{center}
        \parbox{0.8\textwidth}{
        \begin{mathpar}
          \Gamma,s\ts V\gets E \opto \cdots \opto \Gamma',t',V\gets n \opto \cdots \opto \Gamma'\cup\Gamma'',t''\setminus t',x\gets n \opto \Gamma'\cup\Gamma'',(t''\setminus t'\vert x\mapsto n)\,,
        \end{mathpar}}
      \end{center}
      where we have $(t''\setminus t'\vert x\mapsto n)\vert_\Gamma=(s''\vert x\mapsto n)$.
    \item Suppose that the last step in the derivation is
      \[
        \inferrule*
        {
          \Gamma,s\ts V \converges x,s'
        }
        {
          \Gamma,s\ts \oc V \converges s'(x),s'
        }\,.
        \]
      Then, by the induction hypothesis, we have a small-step derivation
      \[
        \Gamma,s\ts V \opto \cdots \opto \Gamma',t'\ts x\,,
        \]
      where $t'\vert_\Gamma=s'$.  
      Then we may compose this derivation pointwise with the evaluation context $\oc-$, and add an extra term on the end, to arrive at the derivation
      \[
        \Gamma,s\ts \oc V \opto \cdots \opto \Gamma',t'\ts \oc x \opto \Gamma',t'\ts t'(x)\,,
        \]
      where $t'(x)=s'(x)$.
    \item Lastly, suppose that the last step in the derivation is
      \[
        \inferrule*
        {
          \Gamma,x,(s\vert x\mapsto 0) \ts M \converges c,(s'\vert x\mapsto n)
        }
        {
          \Gamma,s \ts \neww \lambda x.M \converges c,s'
        }\,.
        \]
      By the induction hypothesis, we have a small-step derivation
      \[
        \Gamma,x,(s\vert x\mapsto 0) \ts M \opto \cdots \opto \Gamma',x,(t'\vert x\mapsto n),c\,,
        \]
      where $t'\vert_\Gamma=s'$.  
      Then we may add a term at the beginning to give us
      \[
        \Gamma,s \ts \neww \lambda x.M \opto \Gamma,x,(s\vert x\mapsto 0) \ts M \opto \cdots \opto \Gamma',x,(t'\vert x\mapsto n),c\,,
        \]
      where $(t'\vert x\mapsto n) \vert_\Gamma=s'$.\qedhere
  \end{itemize}
\end{proof}

@@

Given $\Gamma$, we have a morphism $\cell^n\from \oc S_\Gamma \implies \oc V_\Gamma$, given by
\[
  \oc S_\Gamma \cong \oc \bN \tensor \cdots \tensor \oc \bN \xrightarrow{\cell \tensor \cdots \tensor \cell} \oc \Varr \tensor \cdots \tensor \oc \Varr \cong \oc V_\Gamma\,.
  \]
\begin{lemma}
  For $j=1,\cdots,n$, the following diagram commutes.
  \[
    \begin{tikzcd}
      \oc S_\Gamma \arrow[r, "\cell^n"] \arrow[d, "\oc\pr_j"']
        & \oc V_\Gamma \arrow[d, "\oc \pr_j"] \\
      \oc \bN \arrow[r, "\cell"]
        & \oc \Varr
    \end{tikzcd}
    \]
\end{lemma}
\begin{proof}
  We have a commutative diagram
  \[
    \begin{tikzcd}[column sep=40pt, row sep=40pt]
      \oc S_\Gamma \arrow[r, Isom] \arrow[dr, "\oc \pr_j"']
        & \oc \bN \tensor \cdots \tensor \oc \bN \arrow[r, "\cell \tensor \cdots \tensor \cell"] \arrow[d, "() \tensor \cdots \tensor \oc\bN \tensor \cdots \tensor ()"' {description, xshift=10pt}]
          & \oc \Varr \tensor \cdots \tensor \oc \Varr \arrow[r, Isom] \arrow[d, "() \tensor \cdots \tensor \oc\Varr \tensor \cdots \tensor ()" {description, xshift=-10pt}]
            & \oc V_\Gamma \arrow[dl, "\oc \pr_j"] \\
      %
        & \oc\bN \arrow[r, "\cell"]
          & \oc\Varr
            &
    \end{tikzcd}\,,
    \]
  where the outer triangles commute because the vertical arrows are the projections in the tensor product of comonoids.
\end{proof}

@@

We start our proof of soundness with a result about evaluation contexts.
This result captures the fact that the term filling the hole of an evaluation context is the first thing to be computed, using the sequoid operator to capture this notion of precedence.
\begin{lemma}
  Let $\Gamma\ts M\from T$ be an Idealized Algol term-in-context, and let $\EE$ be an evaluation context with a hole of type $T$, where $\EE[M]\from U$.  
  Then there is a game $A$ and strategies $\sigma\from \oc\V_\Gamma \implies A$, $\tau\from\deno{T}\sequoid A \implies \deno{S}$ such that $\tau$ is a strict strategy and the denotation $\deno{\Gamma\ts\EE[M]}$ factors as
  \[
    \oc\V_\Gamma \xrightarrow{\mu_{\V_\Gamma}} \oc \V_\Gamma \tensor \oc \V_\Gamma \xrightarrow{\deno{\Gamma\ts M}\tensor\sigma} \deno{T}\tensor A \xrightarrow{\wk_{\deno{T},A}} \deno{T} \sequoid A \xrightarrow{\tau} \deno{U}\,.
    \]
  \label{LemEvContexLemma}
\end{lemma}
\begin{proof}
  Structural induction on $\EE$.
  \begin{itemize}
    \item If $\EE=-$ is a hole, then we may take $A=I$, $\sigma=()$ and $\tau=\run_{\deno T}$.

@@

          \begin{tikzcd}[ampersand replacement=\&, column sep=78pt, row sep=20pt]

@@

        \caption[The property in Lemma \ref{LemEvContexLemma} is preserved by conditionals.]{The property in Lemma \ref{LemEvContexLemma} is preserved by sequencing and variable assignment.
        We use the fact that $\eta\in\{\If_X,\IfO_X\}$ is a strict strategy, and that the $\Lambda_s\inv$ is a function from strict strategies to strict strategies, so that $\Lambda_s\inv(\eta)$ is well-defined.}

@@

\begin{lemma}
  Suppose that $\Gamma,s\ts M \oopto \Gamma',s'\ts N$, where $M,N$ have type $T$.
  Then the following diagram commutes.
  \[
    \begin{tikzcd}[column sep=40pt]
      I \arrow[r, "\oc \deno s"] \arrow[d, "\oc \deno s'"']
        & \oc S_\Gamma \arrow[r, "\cell^n"]
          & \oc V_\Gamma \arrow[r, "\mu_{V_\Gamma}"]
            & \oc V_\Gamma \tensor \oc V_\Gamma \arrow[d, "\deno{\Gamma\ts M}\tensor \oc V_\Gamma"] \\
      \oc \bN \arrow[d, "\cell^n"']
        &
          &
            & \deno T \tensor \oc V_\Gamma \arrow[d, "{\wk_{\deno T,\oc V_\Gamma}}"] \\
      \oc V_\Gamma \arrow[r, "\mu_{V_\Gamma}"]
        & \oc V_\Gamma \tensor \oc V_\Gamma \arrow[r, "\deno{\Gamma\ts N} \tensor \oc V_\Gamma"]
          & \deno T \tensor \oc V_\Gamma \arrow[r, "{\wk_{\deno T,\oc V_\Gamma}}"]
            & \deno T \sequoid \oc V_\Gamma
    \end{tikzcd}
    \]
\end{lemma}
\begin{proof}
  \begin{itemize}
    \item For most of the rules, 
  \end{itemize}
\end{proof}

>>>>

The most important feature of strategies of the form $(\sigma_x)$ is the most obvious one: given $X$, and $y\in X$, we have a strategy $y$ for the game $X$ with maximal play $qx$.  
Then $y;(\sigma_x) = \sigma_y$.

@@

This time, instead of defining a relation $\Gamma,s\ts M\converges c,s'$, we define a relation $\Gamma,s\ts M\opto \Gamma,\Delta,s'\ts M'$, where
\begin{itemize}
  \item $\Gamma,\Delta$ are disjoint $\Var$-contexts; 
  \item $s$ is a $\Gamma$-store and $s'$ a $\Gamma,\Delta$-store;  and
  \item $\Gamma\ts M$, $\Gamma,\Delta\ts M'$ are Idealized Algol terms-in-context.
\end{itemize}

@@

Next, we define a relation $\Gamma,s,M\oopto\Gamma,\Delta,s',M'$ as in Figure \ref{FigIaSsOpSem}.

We then define the relation $\opto$ as
\[
  \inferrule*{ \Gamma,s\ts M\oopto \Gamma,\Delta,s'\ts M'}{\Gamma,s\ts \EE[M] \opto \Gamma,\Delta,s'\ts\EE[M']}
  \]
for each evaluation context $\EE$.

\begin{figure}
  \begin{mathpar}
    \Gamma,s\ts (\lambda x.M)N \oopto \Gamma,s\ts M[N/x]
    \and
    \Gamma,s\ts \Y M \oopto \Gamma,s\ts M(\Y M)
    \and
    \Gamma,s\ts \suc n \oopto \Gamma,s\ts n+1
    \\
    \Gamma,s \ts \pred (n+1) \oopto \Gamma,s\ts n
    \and
    \Gamma,s\ts \pred 0 \oopto \Gamma,s\ts 0
    \\
    \Gamma,s\ts \skipp;M \oopto \Gamma,s\ts M
    \\
    \Gamma,s\ts \If \true \Then N \Else P \oopto \Gamma,s\ts N
    \and
    \Gamma,s\ts \If \false \Then N \Else P \oopto \Gamma,s\ts P
    \and
    \Gamma,s\ts \IfO 0 \Then N \Else P \oopto \Gamma,s\ts N
    \and
    \Gamma,s\ts \IfO (n+1) \Then N \Else P \oopto \Gamma,s\ts P
    \and
    \Gamma,s\ts x \gets n \oopto \Gamma,(s\vert x\mapsto n)\ts \skipp
    \and
    \Gamma,s\ts \oc x \oopto \Gamma,s\ts s(x)
    \\
    \Gamma,s\ts \neww \lambda x.M \oopto \Gamma,x,(s\vert x\mapsto 0)\ts M
    \\
    \Gamma,s \ts (\mkvar W\,R) \gets n \oopto \Gamma,s\ts Wn
    \and
    \Gamma,s \ts \oc(\mkvar W\,R) \oopto \Gamma,s\ts R
  \end{mathpar}
  \caption{Felleisen-style small-step operational semantics for Idealized Algol.}
  \label{FigIaSsOpSem}
\end{figure}

We need to prove that this is equivalent to our original semantics.
Given a $\Gamma,\Delta$-store $s$, write $s\vert_{\Gamma}$ for the restriction of $s$ to $\Gamma$.

\begin{lemma}
  Suppose that $\Gamma,s\ts M \oopto \Gamma,\Delta,s'\ts M'$ and that $\Gamma,\Delta,s'\ts \EE[M'] \converges c,s''$.  
  Then $\Gamma,s\ts \EE[M]\converges c,s''\vert_\Gamma$.
  \label{LemSmallToBig}
\end{lemma}
\begin{proof}
  Structural induction on $\EE$.
  The base case, when $\EE$ is a hole, covers the interesting cases, so we shall leave it to last.
  The remaining cases are quite similar, so we will show the proof for one of them for illustration.

  If $\EE=\EE'\,N$, for some term $N$, then we have $\Gamma,\Delta,s'\ts \EE'[M']\,N\converges c,s''$.  
  By inspection of the rules in Figure \ref{FigIaOpSem}, the derivation of this must end with a rule of the form
  \[
    \inferrule*{\Gamma,\Delta,s'\ts \EE'[M'] \converges \lambda x.M'',t \\ \Gamma,\Delta,t \ts M''[N/x] \converges c,s''}
    {\Gamma,\Delta,s'\ts \EE'[M']\,N \converges c,s''}\,.
    \]
  Thus, $\Gamma,\Delta,s'\ts \EE'[M']\converges \lambda x.M'',t$ and $\Gamma,\Delta\ts M''[N/x]\converges c,s''$ must be provable for some $M'',t$.
  By the induction hypothesis, this means that $\Gamma,s\ts \EE'[M]\converges \lambda x.M'',t$ is provable.
  Then we have a derivation
  \[
    \inferrule*{\Gamma,\Delta,s\ts \EE'[M] \converges \lambda x.M'',t \\ \Gamma,\Delta,t \ts M''[N/x] \converges c,s''}
    {\Gamma,\Delta,s\ts \EE'[M]\,N\converges c,s''\vert_{\Gamma,\Delta}}\,.
    \]
  Then, because any variables in $\Delta$ are not mentioned in $\EE'[M]\,N$ or in $c$, we have
  \[
    \Gamma,s\ts \EE'[M]\,N\converges c,s''\vert_\Gamma\,.
    \]
  Now, let us suppose that $\EE$ is a hole, so that $\EE[M']=M'$.

@@

  \begin{itemize}
    \item Suppose that the last step in the derivation is
      \[
        \inferrule*{ }
        {\Gamma,s\ts c\converges c,s}\,.
        \]
      Then we have the one-element sequence $\Gamma,s\ts c$.  
    \item Suppose that the last step in the derivation is
      \[
        \inferrule*
        {
          \Gamma,s\ts M\converges \lambda x.M',s' \\ \Gamma,s' \ts M'[N/x]\converges c,s''
        }
        {
          \Gamma,s \ts MN\converges c,s''
        }\,.
        \]
      Then, by the inductive hypothesis, we have small-step derivations
      \begin{mathpar}
        \Gamma,s \ts M \opto \cdots \opto \Gamma,\Delta,t',\lambda x.M'
        \and
        \Gamma,s' \ts M'[N/x]\opto \cdots \opto \Gamma,\Delta',t'',c\,,
      \end{mathpar}
      where $t'\vert_\Gamma=s'$ and $t''\vert_\Gamma=s''$.

      If we apply the evaluation context $-N$ pointwise to the first small-step derivation, then we have another valid small-step derivation.  
      Then we can join the two together to get the derivation
      \begin{center}
        \parbox{0.8\textwidth}{
        \begin{mathpar}
          \Gamma,s \ts MN \opto \cdots \opto \Gamma,\Delta,t',(\lambda x.M')N \opto \Gamma,\Delta,t',M'[N/x] \opto \cdots \opto \Gamma,\Delta\cup\Delta',t''\setminus t',c\,,
        \end{mathpar}}
      \end{center}
      where $t''\setminus t'$ is the $\Gamma,\Delta\cup\Delta'$-store that agrees with $t''$ on $\Gamma,\Delta'$ and with $t'$ on $\Delta\setminus\Delta'$.
      Then $(t''\setminus t')\vert_{\Gamma}=s''$.
    \item Suppose that the last step in the derivation is
      \[
        \inferrule*
        {
          \Gamma,s\ts E\converges n,s' \\ \Gamma,s'\ts V\converges x,s''
        }
        {
          \Gamma,s \ts V \gets E \converges\skipp,(s''\vert x\mapsto n)
        }\,.
        \]
      By the inductive hypothesis, we have small-step derivations
      \begin{mathpar}
        \Gamma,s\ts E \opto \cdots \opto \Gamma,\Delta,t',n
        \and
        \Gamma,s'\ts V \opto \cdots \opto \Gamma,\Delta',t'',x\,,
      \end{mathpar}
      where $t'\vert_{\Gamma}=s'$ and $t''\vert_{\Gamma}=s''$.

      We may apply the evaluation context $V\gets-$ pointwise to the first derivation and the evaluation context $-\gets n$ pointwise to the second, and then string the two together to get
      \begin{center}
        \parbox{0.8\textwidth}{
        \begin{mathpar}
          \Gamma,s\ts V\gets E \opto \cdots \opto \Gamma,\Delta,t',V\gets n \opto \cdots \opto \Gamma,\Delta\cup\Delta',t''\setminus t',x\gets n \opto \Gamma,\Delta\cup\Delta',(t''\setminus t'\vert x\mapsto n)\,,
        \end{mathpar}}
      \end{center}
      where we have $(t''\setminus t'\vert x\mapsto n)\vert_\Gamma=(s''\vert x\mapsto n)$.
    \item Suppose that the last step in the derivation is
      \[
        \inferrule*
        {
          \Gamma,s\ts V \converges x,s'
        }
        {
          \Gamma,s\ts \oc V \converges s'(x),s'
        }\,.
        \]
      Then, by the induction hypothesis, we have a small-step derivation
      \[
        \Gamma,s\ts V \opto \cdots \opto \Gamma,\Delta,t'\ts x\,,
        \]
      where $t'\vert_\Gamma=s'$.  
      Then we may compose this derivation pointwise with the evaluation context $\oc-$, and add an extra term on the end, to arrive at the derivation
      \[
        \Gamma,s\ts \oc V \opto \cdots \opto \Gamma,\Delta,t'\ts \oc x \opto \Gamma,\Delta,t'\ts t'(x)\,,
        \]
      where $t'(x)=s'(x)$.
    \item Lastly, suppose that the last step in the derivation is
      \[
        \inferrule*
        {
          \Gamma,x,(s\vert x\mapsto 0) \ts M \converges c,(s'\vert x\mapsto n)
        }
        {
          \Gamma,s \ts \neww \lambda x.M \converges c,s'
        }\,.
        \]
      By the induction hypothesis, we have a small-step derivation
      \[
        \Gamma,x,(s\vert x\mapsto 0) \ts M \opto \cdots \opto \Gamma,\Delta,x,(t'\vert x\mapsto n),c\,,
        \]
      where $t'\vert_\Gamma=s'$.  
      Then we may add a term at the beginning to give us
      \begin{center}
        \parbox{0.6\textwidth}{
        \begin{mathpar}
          \Gamma,s \ts \neww \lambda x.M \opto \Gamma,x,(s\vert x\mapsto 0) \ts M \opto \cdots \opto \Gamma,\Delta,x,(t'\vert x\mapsto n),c\,,
        \end{mathpar}}
      \end{center}
      where $(t'\vert x\mapsto n) \vert_\Gamma=s'$.\qedhere
  \end{itemize}
\end{proof}

@@

Given $\Gamma$, we have a morphism $\cell^\Gamma\from \oc S_\Gamma \implies \oc V_\Gamma$, given by
\[
  \oc S_\Gamma \cong \oc \bN \tensor \cdots \tensor \oc \bN \xrightarrow{\cell \tensor \cdots \tensor \cell} \oc \Varr \tensor \cdots \tensor \oc \Varr \cong \oc V_\Gamma\,.
  \]
\begin{lemma}
  For $j=1,\cdots,|\Gamma|$, the following diagram commutes.
  \[
    \begin{tikzcd}
      \oc S_\Gamma \arrow[r, "\cell^\Gamma"] \arrow[d, "\oc\pr_j"']
        & \oc V_\Gamma \arrow[d, "\oc \pr_j"] \\
      \oc \bN \arrow[r, "\cell"]
        & \oc \Varr
    \end{tikzcd}
    \]
\end{lemma}
\begin{proof}
  We have a commutative diagram
  \[
    \begin{tikzcd}[column sep=40pt, row sep=40pt]
      \oc S_\Gamma \arrow[r, Isom] \arrow[dr, "\oc \pr_j"']
        & \oc \bN \tensor \cdots \tensor \oc \bN \arrow[r, "\cell \tensor \cdots \tensor \cell"] \arrow[d, "() \tensor \cdots \tensor \oc\bN \tensor \cdots \tensor ()"' {description, xshift=10pt}]
          & \oc \Varr \tensor \cdots \tensor \oc \Varr \arrow[r, Isom] \arrow[d, "() \tensor \cdots \tensor \oc\Varr \tensor \cdots \tensor ()" {description, xshift=-10pt}]
            & \oc V_\Gamma \arrow[dl, "\oc \pr_j"] \\
      %
        & \oc\bN \arrow[r, "\cell"]
          & \oc\Varr
            &
    \end{tikzcd}\,,
    \]
  where the outer triangles commute because the vertical arrows are the projections in the tensor product of comonoids.
\end{proof}

@@

We start our proof of soundness with a result about evaluation contexts.
This result captures the fact that the term filling the hole of an evaluation context is the first thing to be computed, using the sequoid operator to capture this notion of precedence.
\begin{lemma}
  Let $\Gamma\ts M\from T$ be an Idealized Algol term-in-context, and let $\EE$ be an evaluation context with a hole of type $T$, where $\EE[M]\from U$.  
  Then there is a game $A$ and strategies $\sigma\from \oc\V_\Gamma \implies A$, $\tau\from\deno{T}\sequoid A \implies \deno{S}$, where $\tau$ is a strict strategy, such that the denotation $\deno{\Gamma\ts\EE[M]}$ factors as
  \[
    \oc\V_\Gamma \xrightarrow{\mu_{\V_\Gamma}} \oc \V_\Gamma \tensor \oc \V_\Gamma \xrightarrow{\deno{\Gamma\ts M}\tensor\sigma} \deno{T}\tensor A \xrightarrow{\wk_{\deno{T},A}} \deno{T} \sequoid A \xrightarrow{\tau} \deno{U}\,.
    \]
  \label{LemEvContexLemma}
\end{lemma}
\begin{proof}
  Structural induction on $\EE$.
  \begin{itemize}
    \item If $\EE=-$ is a hole, then we may take $A=I$, $\sigma=()$ and $\tau=\run_{\deno T}$.

@@

          \begin{tikzcd}[ampersand replacement=\&, column sep=78pt, row sep=30pt]

@@

        \caption[The property in Lemma \ref{LemEvContexLemma} is preserved by conditionals.]{The property in Lemma \ref{LemEvContexLemma} is preserved by conditionals.
        We use the fact that $\eta\in\{\If_X,\IfO_X\}$ is a strict strategy, and that the $\Lambda_s\inv$ is a function from strict strategies to strict strategies, so that $\Lambda_s\inv(\Lambda_s\inv(\eta))$ is well-defined.}

@@

\begin{lemma}
  Suppose that $\Gamma,s\ts M \oopto \Gamma,\Delta,s'\ts N$, where $M,N$ have type $T$.
  Then the following diagram commutes.
  \[
    \begin{tikzcd}[column sep=28pt]
      I \arrow[r, "\oc \deno s"] \arrow[d, "\oc \deno s'"']
        & \oc S_\Gamma \arrow[r, "\cell^\Gamma"]
          & \oc \V_\Gamma \arrow[r, "\mu_{\V_\Gamma}"]
            &[22pt] \oc \V_\Gamma \tensor \oc \V_\Gamma \arrow[d, "\deno{\Gamma\ts M}\tensor \oc V_\Gamma"] \\
      {\oc S_{\Gamma,\Delta}} \arrow[d, "{\cell^{\Gamma,\Delta}}"']
        &
          &
            & \deno T \tensor \oc V_\Gamma \arrow[d, "{\wk_{\deno T,\oc \V_{\Gamma,\Delta}}}"] \\
      {\oc \V_{\Gamma,\Delta}} \arrow[d, "{\mu_{\V_{\Gamma,\Delta}}}"']
        &
          &
            &  \deno{T}\sequoid \oc\V_\Gamma \arrow[d, "{\deno{T} \sequoid (\Gamma+0_\Delta)}"] \\
      {\oc \V_{\Gamma,\Delta} \tensor \oc \V_{\Gamma,\Delta}} \arrow[rr, "{\deno{\Gamma,\Delta\ts N} \tensor \oc \V_{\Gamma,\Delta}}"]
        &
          & {\deno T \tensor \oc \V_{\Gamma,\Delta}} \arrow[r, "{\wk_{\deno T,\oc \V_{\Gamma,\Delta}}}"]
            & {{\deno T \sequoid \oc \V_{\Gamma,\Delta}}\,,}
    \end{tikzcd}
    \]
  where $\Gamma+0_\Delta\from \oc \V_\Gamma \to \oc \V_{\Gamma,\Delta}$ is the composite
  \[
    \oc \V_\Gamma \xrightarrow{\runit_{\oc\V_\Gamma}} \oc \V_\Gamma \tensor I \xrightarrow{\oc\V_\Gamma\tensor \oc0} \oc\V_\Gamma \tensor \oc S_\Delta \xrightarrow{\oc\V_\Gamma\tensor \cell^\Delta} \oc \V_\Gamma \tensor \oc \V_\Delta \to \oc \V_{\Gamma,\Delta}\,;
    \]
  i.e., the morphism given by initializing new storage cells to $0$ for all the new variables in $\Delta$.
  \label{LemSoundnessOopto}
\end{lemma}
\begin{proof}
  We prove this on a case-by-case basis.
  \begin{itemize}
    \item For most of the rules, $\Delta=\_$ and $s=s'$; i.e., the rule is of the form
      \[
        \Gamma,s\ts M \oopto \Gamma,s \ts N
        \]
      for some $M,N$.
      In such a case, it suffices to show that $\deno{\Gamma\ts M}=\deno{\Gamma\ts N}$.
      Indeed, we have
      \begin{itemize}
        \item $\deno{\Gamma\ts(\lambda x.M)N} = \deno{\Gamma\ts M[N/x]}$ (by a usual substitution-lemma argument);
        \item $\deno{\Gamma\ts\Y M} = \deno{\Gamma\ts (\lambda F.\lambda f.f(F f)) \Y M} = \deno{\Gamma\ts M(\Y M)}$;
        \item $\deno{\Gamma\ts \suc n} = \deno{\Gamma \ts n+1}$;
        \item $\deno{\Gamma\ts \pred (n+1)} = \deno{\Gamma\ts n}$;
        \item $\deno{\Gamma\ts \pred 0} = \deno{\Gamma\ts 0}$;
        \item $\deno{\Gamma\ts\skipp;M} = \deno{\Gamma\ts M}$;
        \item $\deno{\Gamma\ts\If \true \Then N \Else P} = \deno{\Gamma\ts (\lambda x.\lambda y.x)NP} = \deno{\Gamma\ts N}$;
        \item $\deno{\Gamma\ts\If \false \Then N \Else P} = \deno{\Gamma\ts (\lambda x.\lambda y.y)NP} = \deno{\Gamma\ts P}$;
        \item $\deno{\Gamma\ts\IfO 0 \Then N \Else P} = \deno{\Gamma\ts (\lambda x.\lambda y.x)NP} = \deno{\Gamma\ts N}$;
        \item $\deno{\Gamma\ts\IfO (n+1) \Then N \Else P} = \deno{\Gamma\ts (\lambda x.\lambda y.y)NP} = \deno{\Gamma\ts P}$;
        \item \parbox[t][][t]{0.8\textwidth}{$\deno{\Gamma\ts(\mkvar W\,R)\gets n} = \langle \deno{\Gamma\ts Wn}_{n\in\bN},\deno{\Gamma\ts R}\rangle;\pr_n = \deno{\Gamma\ts Wn}$; and}
        \item $\deno{\Gamma\ts\oc(\mkvar W\,R)} = \langle \deno{\Gamma\ts Wn}_{n\in\bN},\deno{\Gamma\ts R}\rangle;\pr_{\bN} = \deno{\Gamma\ts R}$.
      \end{itemize}
    \item Now consider the rule
      \[
        \Gamma,s\ts\neww \lambda x.M\oopto \Gamma,x,(s\vert x\mapsto 0)\ts M\,,
        \]
      where $\Gamma\ts M\from T$.
      The first observation to make is that the denotation $\deno{\Gamma\ts \neww \lambda x.M}$ may be written as
      \[
        \oc\V_\Gamma \xrightarrow{\Gamma + 0_x} \oc\V_{\Gamma,x} \xrightarrow{\Lambda\inv(\deno{\Gamma \ts \lambda x.M})} \deno{T}\,,
        \]
      where $\Gamma+0_x$ is as defined in the statement of this Lemma.
      Of course, $\Lambda\inv(\deno{\Gamma\ts \lambda x.M})=\deno{\Gamma,x\ts M}$.

      Next, we claim that we have a commutative diagram
        \begin{tikzcd}
          \oc S_\Gamma \arrow[r, "\cell^\Gamma"] \arrow[d, "{\oc\langle S_\Gamma,0\rangle}"']
            & \oc \V_\Gamma \arrow[d, "\Gamma+0_x"] \\
          {\oc S_{\Gamma,x}} \arrow[r, "{\cell^{\Gamma,x}}"]
            & {\oc \V_{\Gamma,x}\,.}
      Indeed, we have the diagram
        \begin{tikzcd}[column sep=2pt, row sep=20pt]
          \oc S_\Gamma \arrow[r] \arrow[dddd, "{\oc\langle S_\Gamma,0\rangle}"' description]
            &[5pt] \oc \bN \tensor \cdots \tensor \oc \bN \arrow[r, "\cell\tensor \cdots \tensor \cell"] \arrow[d, "\runit" description]
              &[10pt] \oc\Varr \tensor \cdots \tensor \oc\Varr \arrow[r] \arrow[d, "\runit" description]
                & \oc\V_\Gamma \arrow[d, "\runit" description] \\
          %
